Manuscript_Github_Pchabaudi_pir_TPMHeatmaps

### 2021-04-26 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
New chab heatmaps file
Heatmap separated by sub-family
Added ancestral bar chart code to see if it should be included

```{r highest_expressed_stage_heatmap_fig3b}

@@

@@

```{r pirs_side-by-side_figure4_RMT-SBP-completelySeparate}

>>>>

```{r highest_expressed_stage_heatmap_fig3c}

@@

# Bar chart of ancestral _pir_ expression.

```{r}
  cir_plot <- twentyfour_rMT %>% 
    filter(Geneid %in% 'PCHAS_0101200') %>% 
    melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
    # mutate(stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = '')) %>%
    mutate(time = str_extract(sample, pattern = '[[:digit:]]{2}h')) %>% 
    group_by(sample, time) %>% 
    dplyr::summarise(sum_tpm = sum(tpm))

y_scale <- seq(0, 
               signif(ceiling(max(cir_plot$sum_tpm)), 
                      digits = 2), 
               length.out = 5)

(
  p <- ggplot(data = cir_plot, 
              aes(x = time, 
                  y = sum_tpm)) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "bar", width = 0.75, size = 0.25, position = 'dodge',
                 fill = 'lightblue') +
    scale_y_continuous(breaks = y_scale) +
    geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
    ylab(as.expression(bquote('Total'~italic(.('PCHAS_0101200'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 0, 
                                   vjust = 0.5,
                                   size = 13))
)

if(global_save_var){
  ggsave2(filename = 'Manuscript_ancestralPir_BarChart.pdf',
          plot = p,
          dpi = 300,
          width = 15,
          height = 10,
          units = 'cm')
}

@@

```{r pirs_side-by-side_figure4}

### 2021-04-26 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir_TPMHeatmaps.Rmd
Added ancestral bar chart code to see if it should be included

>>>>

Add chapl/aapl annotation to above

```{r}

chapl_aapl_name_vec <- ifelse(grepl(cir_info$chapl_aapl_name_num[match(rownames(combined_data_pir_ht), 
                                                                                     cir_info$Geneid)], 
                                                  pattern = 'NA'),
                                            NA,
                                            cir_info$chapl_aapl_name_num[match(rownames(combined_data_pir_ht), cir_info$Geneid)])

annotation_col <- chapl_aapl_name_col_num[ordering(chapl_aapl_name_vec,
                                                   order_vector = 'ChAPL')]

chapl_aapl_name_ha <- rowAnnotation(
  'CHAPL/AAPL' = anno_simple(
    chapl_aapl_name_vec,
    col = annotation_col,
    na_col = 'white'
  ),
  annotation_name_gp = gpar(fontsize = 10)
)

chapl_aapl_name_lgd <- Legend(
  title = 'CHAPL/AAPL',
  at = names(annotation_col)
    # str_subset(
    # sort(
    #   factor(chapl_aapl_name_vec,
    #          ordering(chapl_aapl_name_vec,
    #                   order_vector = 'ChAPL'))
    # )
    # ,
    # pattern = 'NA',
    # negate = TRUE
  # )
,
  legend_gp = gpar(fill = na.omit(annotation_col))
)

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'subfam']),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  # row_title = NULL,
  left_annotation = chapl_aapl_name_ha,
  row_title_rot = 0,
  row_title_gp = gpar(fontsize = 10),
  row_split = forcats::fct_shift(
    relevel(
      as.factor(combined_data_pir_ht$subfam),
      ref = 'ref')
  ),
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  )
)

if(global_save_var){
  pdf(file = 'Interest_SubfamSplit_ChAPL-AAPLAnnotate_heatmap.pdf',
      height = 5,
      width = 5)
draw(ht, 
     row_title_side = 'left',
     column_title_side = 'bottom',
     heatmap_legend_side = 'right',
     annotation_legend_side = 'right',
     annotation_legend_list = list(chapl_aapl_name_lgd),
     merge_legend = TRUE)
  dev.off()
}
